Your Paper Title

### 2025-06-05 Master Thesis/thesis.tex
New

    \vfill
\end{titlepage}
\newpage
\begin{abstract}
\normalsize
\noindent
Name: Su Yingze

@@

This thesis explores tree-level scattering amplitudes in (De)constructed gauge theories using modern on-shell methods. Traditional Feynman diagram techniques, though systematic, become increasingly cumbersome in theories with gauge redundancies and high multiplicity. Motivated by these limitations, we adopt a framework based on analyticity, factorization, and gauge invariance, applying the BCFW recursion relation and related spinor-helicity techniques.

Our analysis focuses on the two-site model, the simplest (De)constructed scenario, which provides a renormalizable four-dimensional realization of dimensional deconstruction and naturally generates Kaluza-Klein (KK)-like spectra. Tree-level color-ordered amplitudes involving massive and massless vector bosons are computed using the BCFW recursion, revealing significant simplifications and cancellation patterns, especially in longitudinal gauge boson scattering. To access non-MHV sectors, we further employ the Cachazo-Svrček-Witten (CSW) expansion, which efficiently constructs NMHV amplitudes from MHV vertices, offering a complementary perspective to BCFW recursion.

Our results demonstrate that on-shell methods remain powerful even in semi-realistic settings with broken gauge symmetry and massive states. The structural simplicity of the resulting amplitudes suggests potential geometric interpretations and invites extensions to loop-level processes.

Future directions include applying generalized unitarity and BCFW-based recursion at loop level, incorporating double-copy constructions to study gravitational analogues, and exploring formulations via the CHY formalism, scattering forms, or positive geometry such as the amplituhedron. These approaches promise deeper insight into the unifying principles behind quantum field theories and the emergence of higher-dimensional behavior from four-dimensional dynamics.

>>>>

    \vfill
\end{titlepage}
\newpage
\begin{abstract}
\normalsize
\noindent
Title: On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory

\noindent
Name: Su Yingze

@@

This thesis studies how to calculate scattering amplitudes in a class of simplified gauge theories known as (De)constructed models, using modern on-shell techniques. In traditional quantum field theory, Feynman diagrams provide a systematic way to compute these amplitudes, but the calculations often become very complicated — especially in gauge theories with many particles or redundant degrees of freedom.

To overcome these difficulties, we use on-shell methods that rely on general principles like momentum conservation, unitarity, and analyticity, rather than directly computing every diagram. A key tool is the BCFW recursion relation, which builds complicated amplitudes from simpler ones by shifting external momenta. We also use the spinor-helicity formalism, which rewrites particle momenta in terms of spinors, making many expressions simpler and more symmetric. To further reduce complexity, we organize our calculations using color ordering, which separates the physics from the gauge group structure.

Our main focus is on the two-site model, a simple setup that mimics extra - dimensional physics using only four-dimensional fields. In this model, we compute various tree-level amplitudes involving both massless and massive gauge bosons. We find interesting simplifications and cancellations, especially in processes involving longitudinal polarization, and confirm that these effects match expectations from higher-dimensional theories. For more complex helicity configurations (beyond MHV), we apply the CSW expansion, which reconstructs amplitudes using MHV building blocks.

Our results show that on-shell techniques are powerful even in models with massive particles and broken symmetries. These compact results hint at deeper geometric structures behind quantum field theory.

Looking forward, this work lays the foundation for further studies, including loop-level calculations, connections to gravity via the double-copy approach, and exploring deeper structures like the CHY formalism, scattering forms, and the amplituhedron, which aim to reformulate quantum field theory in a more elegant and unified way.
